Formalized Linear Programming

### 2019-09-23 TeX/paper.tex
update abstract
Add guidelines sentences to structure our abstract

\begin{document}
\bibliographystyle{plain}
\lstset{language=lean}
\lstset{basicstyle=\normalsize}
\maketitle
\begin{abstract}
  Sentence about applications of simplex. Most simplex solvers are non-verified implementations and are not guaranteed to be correct. They are usually written in languages like C++ which are difficult to certify. One verified implementation exists, but it is not intended to be executable in practice. We implement a formally verified executable simplex solver in the Lean theorem prover. Our implementation uses Bland's rule to select a pivot, and a pivot function stated without any matrix multiplication in contrast to some book proofs on the simplex algorithm.
\end{abstract}

>>>>

\begin{document}
\bibliographystyle{plain}
\lstset{language=lean}
\lstset{basicstyle=\normalsize}
\maketitle
\begin{abstract}
% What is the general topic we look at?
Sentence about applications of simplex.

% What is the specific research problem we face?
Most simplex solvers are non-verified implementations and are not guaranteed to be correct.i

% Why has nobody else adequately answered the research problem yet?
They are usually written in languages like C++ which are difficult to certify.
One verified implementation exists, but it is not intended to be executable in
practice.

% What is our key idea to address the stated research problem?
We implement a formally verified executable simplex solver in the Lean theorem
prover.

% What are the key steps needed to successfully implement our idea?
Our implementation uses Bland's rule to select a pivot, and a pivot
function stated without any matrix multiplication in contrast to some book
proofs on the simplex algorithm.

% What is the outcome of our work?

% What is the key global impact we envision our research to have?
This research demonstrates the practicality of Lean as a language for fast
verified algorithms.

\end{abstract}
